01-deseq2-all

### 2019-03-14 scripts/01-DESeq2-all.Rmd
slim to all, rename all
now with underscores no dash

---
title: "01-deseq2"
output: html_document
---

@@

```{r}
colData <- read.csv("../results/00-colData-characterization.csv", header = T, row.names = 1)
countData <- read.csv("../results/00-countData-characterization.csv", header = T, row.names = 1)
```

@@

pdf(file="../figures/01-pcaplot12.pdf", width=3.3, height=2.5)
plot(PCA12)
dev.off()
```

>>>>

---
title: "01-deseq2-all"
output: md_document
---

@@

```{r}
colData <- read.csv("../results/00_colData_characterization.csv", header = T, row.names = 1)
countData <- read.csv("../results/00_countData_characterization.csv", header = T, row.names = 1)
```

@@

PCA34 <- ggplot(pcadata, aes(pcadata$PC3, pcadata$PC4, color=sextreatment, shape= tissue)) +
    geom_point(size=1.5) +
    xlab(paste0("PC3: ", percentVar[3],"%")) +
    ylab(paste0("PC4: ", percentVar[4],"%")) +
    stat_ellipse(level = 0.95) + 
    theme_cowplot(font_size = 7, line_size = 0.25)  
PCA34

PCA56 <- ggplot(pcadata, aes(pcadata$PC5, pcadata$PC6, color=sextreatment, shape= tissue)) +
    geom_point(size=1.5) +
    xlab(paste0("PC5: ", percentVar[53],"%")) +
    ylab(paste0("PC6: ", percentVar[6],"%")) +
    stat_ellipse(level = 0.95) + 
    theme_cowplot(font_size = 7, line_size = 0.25)  
PCA56

pdf(file="../figures/01-pcaplot12.pdf", width=3.3, height=2.5)
plot(PCA12)
dev.off()

pdf(file="../figures/01-pcaplot56.pdf", width=3.3, height=2.5)
plot(PCA56)
dev.off()
```
